Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-24 model.tex
removed duplicated Yule wording from model.tex

A simple and yet powerful way to capture and exploit the structure of
data is to fit a hyperplane to the dataset and then use that it to
make predictions.  The roots of this approach date back to Yule's 1927
invention of the autoregressive schema~\cite{weigend93}, which
forecasts the next time step through a weighted average of past
observations: $$p_i = \sum_{j=1}^{i-1} a_j x_j$$ The weighting
coefficients $a_i$ are computed using a polynomial of degree $l$ that
is fit to the past $l+1$ values of $x_i$.  To account for noise in the
data, one can add a so-called ``moving average'' term to the model; to
remove nonstationarities, one can detrend the data using a
differencing operation.  A strategy that incorporates all three of
these features is called a \emph{nonseasonal ARIMA model}.  If
evidence of periodic structure is present in the data, a
\emph{seasonal ARIMA model}, which adds a sampling operation that
filters out periodicities, can be a good choice.

>>>>

A simple and yet powerful way to capture and exploit the structure of
data is to fit a hyperplane to the dataset and then use that it to
make predictions.  The roots of this approach date back to the
original autoregressive schema~\cite{weigend93}, which forecasts the
next time step through a weighted average of past observations: $$p_i
= \sum_{j=1}^{i-1} a_j x_j$$ The weighting coefficients $a_i$ are
computed using a polynomial of degree $l$ that is fit to the past
$l+1$ values of $x_i$.  To account for noise in the data, one can add
a so-called ``moving average'' term to the model; to remove
nonstationarities, one can detrend the data using a differencing
operation.  A strategy that incorporates all three of these features
is called a \emph{nonseasonal ARIMA model}.  If evidence of periodic
structure is present in the data, a \emph{seasonal ARIMA model}, which
adds a sampling operation that filters out periodicities, can be a
good choice.
